\plaintitle

### 2017-06-18 papers/IoT2017/intro.tex
no message

\item \textbf{Inference of Future States of a Prosumer} 
 \Abhishek{Is this not
  related to the first point?  Perhaps the first point can be just
  about identity and second point can be specifically about
  consumption patterns.}\Aron{The first point is about to whom
  information might be leaked, and the second point is about the type
  of information. I'll make this more clear.}  Transactions may reveal
  the future energy usage of a prosumer, which could be used to infer
  private information.  For example, a smart home may know that its
  inhabitants will go out in the evening (\emph{e.g.}, by looking at
  their calendar), and it may trade energy futures accordingly in the
  morning.  Without adequate privacy measures, these trades may reveal
  to other prosumers in the microgrid that the inhabitants will not be
  at home later.  Note that energy
  futures, whose delivery may happen several hours after when the
  transaction is made, can play an important role in predicting and
  controlling microgrid load.  In comparison, smart metering reveals
  only current (or past) usage.

@@

In this paper, we \change{describe an overview of the transactive sequence between different components of the systems. We also describe in the detail the structure of these transactions and show how these transactions}{propose \emph{Privacy-preserving Energy Transactions} (PETra), a distributed-ledger based solution that} (1) enables trading energy futures in a
secure and verifiable manner, (2) preserves prosumer privacy, and (3)
enables DSOs to regulate the trading platform and enforce certain
safety rules. 
%
\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}  
We first describe the basic components of a
transactive IoT microgrid and formulate security, safety, and privacy
requirements.  Next, we introduce PETra and describe the
transactions and services used to implement it.  We then
discuss how PETra satisfies the security, safety, and privacy
requirements.  Finally, we give a brief overview of related work and
offer concluding remarks.

>>>>

\item \textbf{Inference of Future States of a Prosumer} 
  Transactions may reveal
  the future energy usage of a prosumer, which could be used to infer
  private information.  For example, a smart home may know that its
  inhabitants will go out in the evening (\emph{e.g.}, by looking at
  their calendar), and it may trade energy futures accordingly in the
  morning.  Without adequate privacy measures, these trades may reveal
  to other prosumers in the microgrid that the inhabitants will not be
  at home later.  Note that energy
  futures, whose delivery may happen several hours after when the
  transaction is made, can play an important role in predicting and
  controlling microgrid load.  In comparison, smart metering reveals
  only current (or past) usage.

@@

In this paper, we \change{describe an overview of the transactive sequence between different components of the systems. We also describe in the detail the structure of these transactions and show how these transactions}{propose \emph{Privacy-preserving Energy Transactions} (PETra), a distributed-ledger based solution that} (1) enables trading energy futures in a
secure and verifiable manner, (2) preserves prosumer privacy, and (3)
enables DSOs to regulate trading and enforce certain
safety rules. 
%
\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}  
We first describe the basic components of a
transactive IoT microgrid and formulate security, safety, and privacy
requirements.  Next, we introduce PETra and describe the
transactions and services used to implement it.  We then
discuss how PETra satisfies the security, safety, and privacy
requirements.  Finally, we give a brief overview of related work and
offer concluding remarks.

### 2017-06-18 papers/IoT2017/paper.tex
update
no message

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
\usepackage[textsize=tiny, textwidth=1.3cm]{todonotes}
\newcommand{\TODO}[1]{\todo[inline]{#1}}
\newcommand{\Abhishek}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}
\newcommand{\Aron}[1]{\todo[color=green!40, linecolor=black!50]{\textbf{Aron}: #1}}
\newcommand{\Doug}[1]{\todo[color=red!40, linecolor=black!50]{\textbf{Doug}: #1}}

\usepackage[normalem]{ulem}
\newcommand{\change}[2]{\textcolor{red}{\sout{#1}} \textcolor{blue}{#2}}
%\newcommand{\change}[2]{#2} % DO NOT DISPLAY CHANGES

@@

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which may arrange
local communities into transactive microgrids.  Within a transactive
microgrid, consumers with energy generation and storage capabilities
can trade energy with each other, thereby smoothing the load on the
main grid using local supply. However, it is hard to provide
security, safety, and privacy in a decentralized and transactive
energy system.  On the one hand, consumers' personal information must
be protected from their trade partners and \Abhishek{To what extent is
  this different that the information already known by the system
  operator? Is this more related to the ``real-time'' nature of
  transactive information?  Rather than aggregative total information
  which is available at the end of billing cycle today.} \Aron{Do we
  need to detail this in the abstract?}\Abhishek{we dont have to} the
system operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes \change{our}{\emph{Privacy-preserving Energy Transactions} (PETra), a} secure and safe solution for
transactive microgrids, which enables consumers to trade energy
without sacrificing their privacy.  \change{Our solution}{PETra} builds on distributed
ledgers, such as blockchains, and provides anonymity for
communication, bidding, and trading.
\end{abstract}

>>>>

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
\usepackage[textsize=tiny, textwidth=1.3cm, disable]{todonotes}
\newcommand{\TODO}[1]{\todo[inline]{#1}}
\newcommand{\Abhishek}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}
\newcommand{\Aron}[1]{\todo[color=green!40, linecolor=black!50]{\textbf{Aron}: #1}}
\newcommand{\Doug}[1]{\todo[color=red!40, linecolor=black!50]{\textbf{Doug}: #1}}

%\usepackage[normalem]{ulem}
%\newcommand{\change}[2]{\textcolor{red}{\sout{#1}} \textcolor{blue}{#2}}
\newcommand{\change}[2]{#2} % DO NOT DISPLAY CHANGES

@@

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which may arrange
local communities into transactive microgrids.  Within a transactive
microgrid, consumers with energy generation and storage capabilities
can trade energy with each other, thereby smoothing the load on the
main grid using local supply. However, it is hard to provide
security, safety, and privacy in a decentralized and transactive
energy system.  On the one hand, consumers' personal information must
be protected from their trade partners and the
system operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes \change{our}{\emph{Privacy-preserving Energy Transactions} (PETra), a} secure and safe solution for
transactive microgrids, which enables consumers to trade energy
without sacrificing their privacy.  \change{Our solution}{PETra} builds on distributed
ledgers, such as blockchains, and provides anonymity for
communication, bidding, and trading.
\end{abstract}

### 2017-06-18 papers/IoT2017/prelim.tex
no message

%!TEX root = paper.tex
\section{System Model and Requirements}
\Aron{Redundant, previous and following paragraphs state what we do here anyway.}
This section describes a basic system model of transactive IoT
microgrids and formulates security, safety, and privacy requirements.

\subsection{Transactive Microgrid System Model}
\Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
We begin by describing a basic system model of decentralized 
\Doug{Abhishek, if there's room can we add a diagram showing how all these components relate to each other?} 
transactive IoT microgrids.  We discuss the following components: a
distributed ledger for recording transactions, a bid storage service
that facilitates finding trade partners, a microgrid controller for
regulating the microgrid load, and smart meters for measuring the
prosumers' energy production and consumption.
Figure~\ref{fig:softwareArchitecture} shows the high-level architecture of 
\change{our solution.  In this figure, components marked red are introduced to
provide privacy in a safe and secure manner, whereas components marked
in blue are typical elements of a decentralized transactive microgrid.}{a decentralized transactive microgrid with PETra. 
Components marked in blue are basic elements of the decentralized transactive microgrid,
while components marked in red are added (or extended) by PETra.}

@@

\subsubsection{Safety}
A careless or malicious prosumer may destabilize the grid by promising
to produce (or consume) a large amount of energy, but failing to actually
produce (or consume) it.  A significant difference between promised and
actual energy production (or consumption) can result in a large gap
between the aggregate production and consumption of the microgrid.
A large gap threatens the stability of not only the microgrid but also the main
power grid.  Therefore, prosumers should not be able to trade large
amounts of energy that they are unlikely to deliver.
Specifically, we require that 
\begin{itemize}[noitemsep,topsep=-\parskip]
\item the net amount of energy sold (or bought) by a prosumer is upper
  bounded (by an amount set by the DSO), where the net amount of
  energy sold is the difference between the amount of energy sold and
  bought by the prosumer, and the net amount of energy bought is
  defined analogously. %,
%\item the energy bids and asks posted by a prosumer are limited in a similar way.
\end{itemize}

>>>>

%!TEX root = paper.tex
\section{System Model and Requirements}
\change{This section describes a basic system model of transactive IoT
microgrids and formulates security, safety, and privacy requirements.}{A microgrid is a collection of prosumers (residential nodes) that are arranged within the same distribution feeder which supports exchange of power between them. A prosumer node typically includes a smart inverter and a smart meter, which control the flow of power into and out of the prosumer. Additionally, the microgrid contains a set of 
protection nodes that are  responsible for isolating faults on the feeder. Finally, a set of switching nodes, which are operated by the Distribution System Operator (DSO), control the connection of the microgrid to the rest of the distribution system. The DSO is responsible for regulating the net electric power into and out of the microgrid. Starting from this model, we next introduce the transactive microgrid model.}

\subsection{Transactive Microgrid System Model}
\Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
We now describe a basic system model of decentralized 
\Doug{Abhishek, if there's room can we add a diagram showing how all these components relate to each other?} 
transactive IoT microgrids.  We discuss the following components: a
distributed ledger for recording transactions, a bid storage service
that facilitates finding trade partners, a microgrid controller for
regulating the microgrid load, and smart meters for measuring the
prosumers' energy production and consumption.
Figure~\ref{fig:softwareArchitecture} shows the high-level architecture of 
\change{our solution.  In this figure, components marked red are introduced to
provide privacy in a safe and secure manner, whereas components marked
in blue are typical elements of a decentralized transactive microgrid.}{a decentralized transactive microgrid with PETra. 
Components marked in blue are basic elements of the decentralized transactive microgrid,
while components marked in red are added (or extended) by PETra.}

@@

\subsubsection{Safety}
A careless or malicious prosumer may destabilize the grid by promising
to produce (or consume) a large amount of energy, but failing to actually
produce (or consume) it.  A significant difference between promised and
actual energy production (or consumption) can result in a large gap
between the aggregate production and consumption of the microgrid.
A large gap threatens the stability of not only the microgrid but also the main
power grid.  Therefore, prosumers should not be able to trade large
amounts of energy that they are unlikely to deliver.
Specifically, we require that 
\begin{itemize}[noitemsep,topsep=-\parskip]
\item the net amount of energy sold (or bought) by a prosumer is upper
  bounded (by an amount set by the DSO), where the net amount of
  energy sold is the difference between the amount of energy sold and
  bought by the prosumer, and the net amount of energy bought is
  defined analogously. %,
\Aron{If we have space, add back the safety requirement on the bid storage (and also add back the relevant parts of the description of the trading workflow and the ``analysis.''}
%\item the energy bids and asks posted by a prosumer are limited in a similar way.
\end{itemize}

### 2017-06-18 papers/IoT2017/solution.tex
no message

\begin{figure*}[h]
\center
\begin{tikzpicture}[x=3.8cm, y=1.6cm, font=\small,
  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
  entity/.style={draw, align=center, rounded corners=0.1cm},
  asset/.style={midway, align=center},
  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
]
\node[entity] (smartmeter) at (0, 1) {smart meter};
\node[entity] (prosumer1) at (1, 1) {prosumer};
\node[system] (mixing1) at (1.9, 1) {mixing\\service};
\node[entity] (prosumer2) at (3, 1) {prosumer\\(anonymous address)};
\node[system] (bidstorage) at (4, 0.5) {bid\\storage};
\node[entity] (partner) at (3, 0) {other prosumer};
\node[entity] (prosumer3) at (1.5, 0) {prosumer\\(anonymous address)};
\node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right, xshift=-1.5em, yshift=0.5em] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
Note that to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing, which we have omitted from the figure for clarity of presentation.}
\label{fig:sellFlow}
\end{figure*}

@@

The prosumer can now engage in energy trading anonymously.  To find a
trade partner, it can either post an \emph{energy ask} on the bid
storage, or simply search the storage for an acceptable \emph{energy
  bid}.  To post an energy ask, the prosumer first proves to the
storage service---without revealing its original identity---that it
owns a production asset stored at an anonymous address.  It can then
post the energy ask \circled{4}, which contains an anonymous
communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference
to the production asset.  If another prosumer, who is seeking to buy energy,
finds the ask acceptable it can contact the seller using the
communication identifier included in the ask.

>>>>

\begin{figure*}[h]
\centering
\begin{tikzpicture}[x=3.8cm, y=1.6cm, font=\small,
  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
  entity/.style={draw, align=center, rounded corners=0.1cm},
  asset/.style={midway, align=center},
  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
]
\node[entity] (smartmeter) at (0, 1) {smart meter};
\node[entity] (prosumer1) at (1, 1) {prosumer};
\node[system] (mixing1) at (1.9, 1) {mixing\\service};
\node[entity] (prosumer2) at (3, 1) {prosumer\\(anonymous address)};
\node[system] (bidstorage) at (4, 0.5) {bid\\storage};
\node[entity] (partner) at (3, 0) {other prosumer};
\node[entity] (prosumer3) at (1.5, 0) {prosumer\\(anonymous address)};
\node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right, xshift=-1.5em, yshift=0.5em] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, above] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
Note that to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing, which we have omitted from the figure for clarity of presentation.}
\label{fig:sellFlow}
\end{figure*}

@@

The prosumer can now engage in energy trading anonymously.  To find a
trade partner, it can either post an \emph{energy ask} on the bid
storage, or simply search the storage for an acceptable \emph{energy
  bid}.  To post an energy ask, the prosumer first proves to the
storage service---without revealing its original identity---that it
owns a production asset stored at an anonymous address. 
\Aron{This sentence was added because we removed the relevant safety requirement.}
Proving ownership prevents the prosumer from ``spamming'' the storage service with bogus asks.
The prosumer can then
post the energy ask \circled{4}, which contains an anonymous
communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference
to the production asset.  If another prosumer, who is seeking to buy energy,
finds the ask acceptable it can contact the seller using the
communication identifier included in the ask.

### 2017-06-18 papers/IoT2017/transactions.tex
no message

In the previous subsection, we gave an overview of how transactions
are used in the trading workflow to transfer various assets.  We now
describe the format of these transactions, as well as the rules that
they have to satisfy to be valid and recorded on the ledger.  We also
introduce and detail the format of regulatory transactions, which the
DSO uses to regulate the microgrid.\Abhishek{We need a figure describing the transactive system architecture. A collection of agents, arranged in a microgrid and a collection of microgrids being controlled by a DSO after the introduction}

\subsubsection{Timing}

The ability to specify points or intervals in time is crucial.  For
example, control signals specify how the microgrid load should change
at certain points in time, energy trades specify when energy will be
consumed or produced, etc.  To facilitate representing signals and
transactions, we divide time into fixed-length intervals, and specify
points or periods in time using these discrete timesteps.  The length
of the time interval is determined based on the timing assumptions of
the physical power system.  For example, the default length of the
time interval may be 4 seconds, which corresponds to how frequently
the control signal of the DSO typically changes.  \Abhishek{We need to
  add citation here. I will add that tomorrow.}  \Abhishek{What about
  the deadline within which the transactions should finish? Do we need
  to say anything here?}  \Aron{Ideally, we should discuss the timing
  constraints of the ledger (probably when we introduce it), but we
  would first need to make space for this discussion.}

@@

\subsubsection{Energy and Financial Transactions}

Energy and financial transactions transfer energy and financial assets
from one address to another.  Prosumers can use these transactions for
multiple purposes, {\em e.g.}, to trade energy by exchanging assets
with other prosumers, to prove to the bid storage service that they
possess an asset, to hide their identity by transferring assets to and
from mixing services, and to deposit assets at their smart meter.
%
An energy and financial transaction contains the following fields:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item \field{EPA\_in}: list of EPA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an EPA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{ECA\_in}: list of ECA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an ECA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{FA\_in}: list of FA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an FA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{EPA\_out}: list of EPA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{EPA}: an energy production asset,
\item \field{address}: address to which EPA is transferred,
\end{itemize}
\item \field{ECA\_out}: list of ECA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{ECA}: an energy consumption asset,
\item \field{address}: address to which ECA is transferred,
\end{itemize}
\item \field{FA\_out}: list of FA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{FA}: a financial asset,
\item \field{address}: address to which FA is transferred.
\end{itemize}
\end{itemize}
\vspace{0.5\parskip} This transaction transfers the assets specified
in the input lists to the addresses specified in the output lists.
Input and output lists may differ in length, so one asset may be
divided into multiple assets, and multiple assets may be combined into
one.

An energy and financial transaction is valid (and can be recorded on
the ledger) if the following three conditions hold.
\begin{itemize}[noitemsep,topsep=-\parskip]
\item None of the outputs referenced by the inputs have been spent by
  a transaction that has been recorded on the ledger.
\item All signatures are valid, which ensures that an asset can be
  transferred only by its current owner. 
% current owner can transfer an asset. 
\item For each asset type (and for each timestep), the sums of the
input and output assets are equal.  For example, in the case of
energy production assets, the condition is
\begin{align*}
& \forall t: \sum_{\substack{out \,\in\, \field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
& = \sum_{\substack{in \,\in\, \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
%
%& \forall t: \sum_{out \in \field{EPA\_out}} out.\field{EPA}.\field{power} \cdot 1_{\left\{out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}\right\}} \nonumber \\
%& = \sum_{in \in \field{EPA\_in}} in.\field{out}.\field{EPA}.\field{power} \cdot 1_{\left\{in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}\right\}} ,
\end{align*}
%where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
%\begin{equation}
%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
%\end{equation}
The conditions for consumption and financial assets can be described
formally in similar ways.
\end{itemize}
%If a transaction submitted to the ledger is valid, it will be permanently recorded.

@@

The DSO uses regulatory transactions for two purposes: (1) to manage
the set of authorized smart meters and (2) to change the price policy.
%First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
First, whenever a new smart meter is installed, the DSO notifies the
microgrid by authorizing the device using a regulatory transaction.
Likewise, whenever a smart meter is deactivated (\emph{e.g.}, because
service is stopped or the device is believed to be faulty or
compromised), the DSO notifies the microgrid by banning the device.
Second, to influence microgrid load, the DSO can set a price policy,
which includes a price at which prosumers may buy energy from the DSO
and a price at which they may sell energy to the DSO.

@@

A regulatory transaction of this type is valid if 
%the following two conditions hold:
%\begin{compactitem}
%\item 
\field{timestep} is not in the past and 
% specified in the transaction is in the future.
%\item 
the DSO's signature is valid.
%\end{compactitem}
%
The active prices for timestep $t$ are given by the last regulatory
transaction recorded on the ledger whose \field{time} is less than
$t$.  Likewise, regulatory transactions that are recorded on the
ledger later override the authorizations and bans of earlier
transactions.

>>>>

In the previous subsection, we gave an overview of how transactions
are used in the trading workflow to transfer various assets.  We now
describe the format of these transactions, as well as the rules that
they have to satisfy to be valid and recorded on the ledger.  We also
introduce and detail regulatory transactions, which the
DSO uses to regulate the microgrid.

\subsubsection{Timing}
The ability to specify points or intervals in time is crucial.  For
example, control signals specify how the microgrid load should change
at certain points in time, energy trades specify when energy will be
consumed or produced, etc.  To facilitate representing signals and
transactions, we divide time into fixed-length intervals, and specify
points or periods in time using these discrete timesteps.  The length
of the time interval is determined based on the timing assumptions of
the physical power system.  For example, the default length of the
time interval may be 4 seconds, which corresponds to how frequently
the control signal of the DSO typically changes.  \Abhishek{We need to
  add citation here. I will add that tomorrow.}  \Abhishek{What about
  the deadline within which the transactions should finish? Do we need
  to say anything here?}  \Aron{Ideally, we should discuss the timing
  constraints of the ledger (probably when we introduce it), but we
  would first need to make space for this discussion.}

@@

\subsubsection{Energy and Financial Transactions}
Energy and financial transactions transfer energy and financial assets
from one address to another.  Prosumers can use these transactions for
multiple purposes, {\em e.g.}, to trade energy by exchanging assets
with other prosumers, to prove to the bid storage service that they
possess an asset, to hide their identity by transferring assets to and
from mixing services, and to deposit assets at their smart meter.
%
An energy and financial transaction contains the following fields:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item \field{EPA\_in}: list of EPA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an EPA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{ECA\_in}: list of ECA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an ECA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{FA\_in}: list of FA inputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{out}: reference to an FA output of a previous transaction,
\item \field{sig}: signature of the referenced output's address,
\end{itemize}
\item \field{EPA\_out}: list of EPA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{EPA}: an energy production asset,
\item \field{address}: address to which EPA is transferred,
\end{itemize}
\item \field{ECA\_out}: list of ECA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{ECA}: an energy consumption asset,
\item \field{address}: address to which ECA is transferred,
\end{itemize}
\item \field{FA\_out}: list of FA outputs, each of which is defined by
\begin{itemize}[leftmargin=0.5em,nosep]
\item \field{FA}: a financial asset,
\item \field{address}: address to which FA is transferred.
\end{itemize}
\end{itemize}
\vspace{0.5\parskip} This transaction transfers the assets specified
in the input lists to the addresses specified in the output lists.
Input and output lists may differ in length, so one asset may be
divided into multiple assets, and multiple assets may be combined into
one.

An energy and financial transaction is valid (and can be recorded on
the ledger) if the following three conditions hold.
\begin{itemize}[noitemsep,topsep=-\parskip]
\item None of the outputs referenced by the inputs have been spent by
  a transaction that has been recorded on the ledger.
\item All signatures are valid, which ensures that an asset can be
  transferred only by its current owner. 
\item For each asset type (and for each timestep), the sums of the
input and output assets are equal.  For example, in the case of
energy production assets, the condition is
\begin{align*}
& \forall t: \sum_{\substack{out \,\in\, \field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
& = \sum_{\substack{in \,\in\, \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
\end{align*}
The conditions for consumption and financial assets can be described
formally in similar ways.
\end{itemize}

@@

The DSO uses regulatory transactions for two purposes: (1) to manage
the set of authorized smart meters and (2) to change the price policy.
First, whenever a new smart meter is installed, the DSO notifies the
microgrid by authorizing the device using a regulatory transaction.
Likewise, whenever a smart meter is deactivated (\emph{e.g.}, because
service is stopped or the device is believed to be faulty or
compromised), the DSO notifies the microgrid by banning the device.
Second, to influence microgrid load, the DSO can set a price policy,
which includes a price at which prosumers may buy energy from the DSO
and a price at which they may sell energy to the DSO.

@@

A regulatory transaction of this type is valid if 
\field{timestep} is not in the past and 
the DSO's signature is valid.
The active prices for timestep $t$ are given by the last regulatory
transaction recorded on the ledger whose \field{time} is less than
$t$.  Likewise, regulatory transactions that are recorded on the
ledger later override the authorizations and bans of earlier
transactions.
